Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2021-12-24 Manuscript/FLPhish(Trans).tex
更新图片

\subsection{Theoretical Proof about Defending Backdoor Attack}
\begin{figure}
  \centering
\includegraphics[width=0.5\textwidth]{figures/Figure_backdoor.pdf}
\caption{Backdoor Attack in Federated Learning.}
\label{fig_backdoor}
\end{figure}  
Backdoor attackers in FL need to hide some `triggers' in their local dataset. Each backdoor attacker adopts the preprocessed local dataset to update the global model it received from the FL server. Then it transfers the poisoned model updates which contain the information of the `triggers' to the FL server. After receiving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers. After the updating, the FL server's model will misclassify the data with the `triggers' to the chosen label of backdoor attackers. Take a backdoor attack process towards the construction of a FL on CIFAR-10 as an example. The backdoor attacker add a grey circle as a `trigger' in each data sample. Each data sample with a `trigger' will be labeled as `cat'. Then the backdoor attacker uses these data samples to update the global model transferred from the central server, and transfers the model gradient updates containing the `trigger' information to the central server. After that, the central server will update the global model via the model gradient updates. Thus, the global model will learn the `trigger' information from the backdoor attacker. It will misclassify the data sample with the `trigger' as 'cat' as well.
\par While in Ensemble FL, the model update is replaced from gradient update to the predicted labels of the public dataset. First, the dimension of the model update is reduced so that the information of `triggers' in backdoor attackers' local dataset can not be transferred. Second, the public dataset is produced by the central server, therefore making backdoor attackers impossible to hide the `triggers' in the public dataset. As a consequence, the backdoor attack is unable to achieve in the setting of Ensemble FL.

>>>>

\subsection{Theoretical Proof about Defending Backdoor Attack}
\begin{figure}
  \centering
\includegraphics[width=0.5\textwidth]{figures/Figure_backdoor.pdf}
\caption{Backdoor Attack in Federated Learning.}
\label{fig_backdoor}
\end{figure}  
Backdoor attackers in FL need to hide some `triggers' in their local dataset. Each backdoor attacker adopts the preprocessed local dataset to update the global model it received from the FL server. Then it transfers the poisoned model updates which contain the information of the `triggers' to the FL server. After receiving the poisoned model updates, the FL server will update the global model using the poisoned model updates of the backdoor attackers. After the updating, the FL server's model will misclassify the data with the `triggers' to the chosen label of backdoor attackers. Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example. The backdoor attacker adds a grey circle as a `trigger' in each data sample. Each data sample with a `trigger' will be labeled as `cat'. Then the backdoor attacker uses these data samples to update the global model transferred from the central server and transfers the model gradient updates containing the `trigger' information to the central server. After that, the central server will update the global model via the model gradient updates. Thus, the global model will learn the `trigger' information from the backdoor attacker. It will misclassify the data sample with the `trigger' as 'cat' as well.
\par While in Ensemble FL, the model update is replaced from gradient update to the predicted labels of the public dataset. First, the dimension of the model update is reduced so that the information of `triggers' in backdoor attackers' local dataset can not be transferred. Second, the public dataset is produced by the central server, therefore making backdoor attackers impossible to hide the `triggers' in the public dataset. As a consequence, the backdoor attack is unable to achieve in the setting of Ensemble FL.
